Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-09 ms.tex
references

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (~\ref{NickPlot2}) and
(2) angular momentum of the infalling gas and consequentiallly the
size of small scale outflows may vary from galaxy to galaxy at fixed
$\Mbh$. The combination of (1) and (2) is capable of explaining much
of the observed sample, especially considering that scatter in $L_{\rm
  X}$ due to variations in $\dot{M}$ is exacerbated by the expectation
that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient
flows. At a wind heating parameter there is an order of magnitude
difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$
and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) which could also lead to
scatter of $\dot{M}$ due to the variation in the Nuker stellar density
profile $\Gamma$ at fixed $M_{\bullet}$. However, \citet{Pellegrini10}
find that the scatter in $L_X$ is similar if one just looks at
core/cusp galaxies separately. There could also be scatter introduced
in using scaling relationships ($\Mbh-\sigma$) and ($\Mbh-L_{\rm
  bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.

@@

Our results also have implications for the environments encountered by
relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
J1644+57 (\citealt{Bloom:2011aa}), we predict gas densities of a $n
\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
rates within the physically expected range $v_{\rm w} \sim 500-1000$
km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
range estimated by modeling the radioa afterglow of {\it Swift}
J1644+57 (\citealt{Metzger+12}, \citealt{Berger+12}).  In fact, the
flattening of the density profile inferred by \citet{Berger+12} on
radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that
seen in our calculations of the gas density profile for core galaxies
(Fig.~\ref{fig:profiles}, solid line).  The CNM density of the host of
{\it Swift} J1644+57 was a factor of 30 times lower than that inferred
by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf
  BDM: whats going on?}  The implications of our models for CNM
profiles for the diversity of radio emission from TDE jets will be
explored further in future work.

>>>>

A more readily addressable test is whether a steady-state accretion
picture is capable of explaining the large scatter of typically 2-3
orders of magnitude in the observed distribution of $L_{X}/L_{\rm
  edd}$ at fixed $M_{\bullet}$.  Scatter is expected to result from at
least two effects: (1) the strong sensitivity of the accretion rate to
the stellar wind velocity, $\dot{M}/\dot{M}_{\rm edd} \propto
v_{w}^{-3.8(-2.4)}$ for core(cusp) galaxies, respectively
(Fig.~\ref{fig:mdot_mass}; eq.~[\ref{eq:eddr_analytic}]) in
combination with the significant dependence of $v_w$ on stochastic
intermittency in the star formation history (~\ref{fig:NickPlot2}) and
(2) angular momentum of the infalling gas and consequentiallly the
size of small scale outflows may vary from galaxy to galaxy at fixed
$\Mbh$. The combination of (1) and (2) is capable of explaining much
of the observed sample, especially considering that scatter in $L_{\rm
  X}$ due to variations in $\dot{M}$ is exacerbated by the expectation
that $\epsilon_{X} \propto \dot{M}$ for radiatively inefficient
flows. At a wind heating parameter there is an order of magnitude
difference between $\dot{M}$ for core and cusp galaxies at fixed $v_w$
and $M_{\bullet}$ (Fig.~\ref{fig:bh_growth}) which could also lead to
scatter of $\dot{M}$ due to the variation in the Nuker stellar density
profile $\Gamma$ at fixed $M_{\bullet}$. However, \citet{Pellegrini10}
find that the scatter in $L_X$ is similar if one just looks at
core/cusp galaxies separately. There could also be scatter introduced
in using scaling relationships ($\Mbh-\sigma$) and ($\Mbh-L_{\rm
  bulge}$) to measure $\Mbh$ as \citet{Miller+2015} do.

@@

Our results also have implications for the environments encountered by
relativistic jets from TDEs.  For low-mass SMBHs $M_{\bullet} \lesssim
10^{7}M_{\odot}$, characterizing those responsible for {\it Swift}
J1644+57 (\citealt{Bloom+2011}), we predict gas densities of a $n
\sim 0.3-3$ cm$^{-3}$ on radial scales of 0.3 pc for wind heating
rates within the physically expected range $v_{\rm w} \sim 500-1000$
km s$^{-1}$ (Fig.~\ref{fig:profiles}).  These values are within the
range estimated by modeling the radioa afterglow of {\it Swift}
J1644+57 (\citealt{Metzger+12}, \citealt{Berger+12}).  In fact, the
flattening of the density profile inferred by \citet{Berger+12} on
radii scales $r \gtrsim 0.4$ pc (their Fig.~6) looks similar to that
seen in our calculations of the gas density profile for core galaxies
(Fig.~\ref{fig:profiles}, solid line).  The CNM density of the host of
{\it Swift} J1644+57 was a factor of 30 times lower than that inferred
by \citet{Quataert:2004a} for SgrA*, a fact we attribute to...{\bf
  BDM: whats going on?}  The implications of our models for CNM
profiles for the diversity of radio emission from TDE jets will be
explored further in future work.
